A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-11-01 paper/paper.tex
paper: mark two more restrf
paper: 01 to LR change

  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\kstar", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

  \begin{equation*}
    \begin{tikzcd}
      01 \arrow[r, dash, "\kstar1"{name=F}] \arrow[d, dash, "0\kstar" left] & 11 \arrow[d, dash, "1\kstar"] \\
      00 \arrow[r, dash, "\kstar0"{name=T, below}] & 10 \\
      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{equation*}
  \begin{array}{llll}
    X_0                                :                & \underbrace{\unittype}_{\framep[0][0]}                                                   & \rightarrow \U \\
    X_1                                :                & \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
    \begin{array}{c}
        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
        \\ \times \\
        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
      \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} & \rightarrow \U                                                                                            \\
    X_2                                :                & \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
        \begin{array}{c}
          \underbrace{\Sigma b: \left(
          \begin{array}{c}
              X_0(\unitpoint)
              \\ \times \\
              X_0(\unitpoint)
            \end{array}
          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
          \\ \times \\
          \underbrace{\Sigma b: \left(
          \begin{array}{c}
              X_0(\unitpoint)
              \\ \times \\
              X_0(\unitpoint)
            \end{array}
          \right).\; \underbrace{X_1 (\unitpoint, b)}_{\filler[1][1]}}_{\filler[1][0]}
        \end{array}
        \right)}_{\layer[2][0]}\right)}_{\framep[2][1]}.\underbrace{\left(
      \begin{array}{c}
        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
          \begin{array}{c}
            a.\tl.L.\hd.L, \\
            a.\tl.R.\hd.L
          \end{array}
          \right)\right)}_{\restrf[2][1][L]}}_{\filler[1][1]}
        \\ \times \\
        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
          \begin{array}{c}
            a.\tl.L.\hd.R, \\
            a.\tl.R.\hd.R
          \end{array}
          \right)\right)}_{\restrf[2][1][R]}}_{\filler[1][1]}
      \end{array}
      \right)}_{\layer[2][1]}}_{\framep[2][2]}
                                                        & \rightarrow \U                                                                                            \\
    \ldots
  \end{array}
\end{equation*}

>>>>

  \begin{equation*}
    \begin{tikzcd}
      L \arrow[r, "\kstar", dash] & R
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

  \begin{equation*}
    \begin{tikzcd}
      LR \arrow[r, dash, "\kstar R"{name=F}] \arrow[d, dash, "L\kstar" left] & RR \arrow[d, dash, "R\kstar"] \\
      LL \arrow[r, dash, "\kstar L"{name=T, below}] & RL \\
      \arrow[rightarrow, from=F, to=T, phantom, "\kstar\kstar" description]
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\begin{equation*}
  \begin{array}{llll}
    X_0                                :                & \underbrace{\unittype}_{\framep[0][0]}                                                   & \rightarrow \U \\
    X_1                                :                & \underbrace{\Sigma \unitpoint: \unittype. \underbrace{\left(
    \begin{array}{c}
        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
        \\ \times \\
        \underbrace{X_0(\unitpoint)}_{\filler[0][0]}
      \end{array}\right)}_{\layer[1][0]}}_{\framep[1][1]} & \rightarrow \U                                                                                            \\
    X_2                                :                & \underbrace{\Sigma a: \underbrace{\left(\Sigma \unitpoint: \unittype. \underbrace{\left(
        \begin{array}{c}
          \underbrace{\Sigma b: \left(
          \begin{array}{c}
              X_0(\unitpoint)
              \\ \times \\
              X_0(\unitpoint)
            \end{array}
          \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][L]}}_{\filler[1][1]}}_{\filler[1][0]}
          \\ \times \\
          \underbrace{\Sigma b: \left(
          \begin{array}{c}
              X_0(\unitpoint)
              \\ \times \\
              X_0(\unitpoint)
            \end{array}
          \right).\; \underbrace{X_1 \underbrace{(\unitpoint, b)}_{\restrf[2][0][R]}}_{\filler[1][1]}}_{\filler[1][0]}
        \end{array}
        \right)}_{\layer[2][0]}\right)}_{\framep[2][1]}.\underbrace{\left(
      \begin{array}{c}
        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
          \begin{array}{c}
            a.\tl.L.\hd.L, \\
            a.\tl.R.\hd.L
          \end{array}
          \right)\right)}_{\restrf[2][1][L]}}_{\filler[1][1]}
        \\ \times \\
        \underbrace{X_1 \underbrace{\left(a.\hd, \left(
          \begin{array}{c}
            a.\tl.L.\hd.R, \\
            a.\tl.R.\hd.R
          \end{array}
          \right)\right)}_{\restrf[2][1][R]}}_{\filler[1][1]}
      \end{array}
      \right)}_{\layer[2][1]}}_{\framep[2][2]}
                                                        & \rightarrow \U                                                                                            \\
    \ldots
  \end{array}
\end{equation*}
